---
title: Anti-PC and Authenticity Performances in Politics in Brazil and the United States
author:
- Henrique Sposito^[PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
date: "3 July 2022"
output:
  pdf_document: default
  fig_caption: yes
  html_document:
    df_print: paged
  word_document:
    reference_docx: template.docx
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
always_allow_html: TRUE
bibliography: references.bib
csl: chicago.csl
abstract: Various politicians have denounced "political correctness" (PC) in discourse. While some scholars argue that anti-PC discourses are populist tools to label elites [@mudde2004] or a form of cultural backlash against liberal changes [@norris2019], these explanations focus on specific manifestations of anti-PC by specific politicians that embody their arguments. Instead, this article argues that anti-PC discourses are performances of authenticity in politics. As authenticity performances, anti-PC discourses reduce the perceived link between thinking and saying for audiences [conway2009]. A framework for identifying several discursive performances of authenticity in politics, beyond anti-PC, that focuses on displays (what), projections (who, when, and where), and mechanisms (how) is developed. A purpose-built dictionary of terms is designed to detect these authenticity performances in large text datasets of campaign remarks, debates, interviews, and official speeches gathered for presidents and presidential candidates at the national level in Brazil and the United States since the 1980s. The analysis indicates that the total frequencies of authenticity performances are not systematically greater in election years, politicians usually perform one or more authenticities above the 95th percentile when they are candidates or after having left office. However, in the case of Brazil, there authenticity performances spiked in politics from 2010 to 2016, the Dilma Rousseff years. Moreover, the variation in types of authenticity performed in time and across cases indicate that contextual conditions make some types of performances more, or less, credible to audiences at junctures so politicians adapt to perform authenticities audiences “want to hear”. Lastly, debates became the setting in which authenticity is performed most frequently, while interviews are the setting in which authenticity is performed least frequently, in both cases in recent years.
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(readxl)
library(ggplot2)
library(readr)
library(stringr)
library(stringi)
library(ggthemes)
library(tm)
library(tidytext)
library(corrplot)
library(Hmisc)
library(ggpubr)
library(plm)
library(modelsummary)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

```{r data, message=FALSE, warning=FALSE, include=FALSE}
# Since some of the text cleaning takes hours to run (i.e. removing punctuation),
# we start with the data that has been merged and cleaned simple cleaning.
# For more information on how the data was merged and the cleaning was done,
# please see the analysis_descriptive script in the under the analysis folder.
BR <- readRDS("~/Documents/GitHub/authenticity_performances/article/BR.Rds") # Brazil data
US <- readRDS("~/Documents/GitHub/authenticity_performances/article/US.Rds") # US data
# Let's create a length column based on number of characters for later on
BR$length <- nchar(BR$text)
US$length <- nchar(US$text)
# Let's also create a date (year) column for later on
BR$date <- stringr::str_extract(BR$doc_id, "[0-9]{4}")
US$date <- stringr::str_extract(US$doc_id, "[0-9]{4}")
# Let' create a setting variable for when data is merged
US$settingc <- paste0(US$setting, "_US")
BR$settingc <- paste0(BR$setting, "_BR")
# Dictionary of terms for authenticity performances for US
truth_telling <- stringr::str_squish("am telling the truth|are telling the truth|is telling the truth|the truth is|this is the truth|not lying|not lies|no lies|not telling you lies|is honest|am honest|is being honest|are being honest|are honest|honesty|is sincere|are sincere|am sincere|is being sincere|are being sincere|is true|are true|not a liar|bottom of my heart|I swear|I reassure|we reassure|I assure|we assure|be assured|is truthful|are truthful|am truthful|is being truthful|are being truthful|I know that|is evident|are evident|I am sure|trust me|am frank|are frank|is frank|being frank|is upfront|are upfront|am upfront|being upfront|will come clean|am coming clean|are coming clean|is straightforward|are straightforward|being straightforward|believe me|I am certain|no bullshit|not bullshitting")
lie_accusations <- stringr::str_squish("not truth|not the truth|not true|aren’t true|isn’t true|being untruthful|is lying|are lying|is a liar|are liars|is dishonest|are  dishonest|being dishonest|is fake|are fake|being fake|is corrupt|are corrupt|full of lies|not sincere|not being sincere|isn’t sincere|aren’t sincere|not honest|not being honest|is cheating|is a cheater|are cheaters|are cheating|are tricking|is tricking|be deceived|is deceiving|are deceiving|are a hypocrite|is a hypocrite|are being a hypocrite|is being a hypocrite|is crooked|are crooked|is misleading|are misleading|has double-standards|are sneaky|is sneaky| has two faces|two-faced|has double faces|double-faced|you are wrong|not correct|fooled by|do not believe|is misrepresenting|they misrepresent|is misrepresent|are misrepresent|pretends that|pretends to|is pretending|are pretending|keep pretending|breach your trust|breach of trust|is false|are false|being false|is misinforming|are misinforming|being misinformed|pretended|cut the crap|full of crap")
consistency <- stringr::str_squish("we delivered|I delivered|check and see|I keep my word|we keep our word|I kept my word|we kept our word|I keep my promise|I kept my promise|we keep our promise|as promised|we kept our promise|am responsible|I take responsibility|we take responsibility|we assume responsibility|we are accountable|we are responsible|our duty|my duty|give my word|giving my word|own up my|owning up my|accept responsibility|accept the blame|recognize my mistakes|admit I was wrong|I made mistakes|I guarantee|we guarantee|I can guarantee|we can guarantee|I promise|we promise|we can prove|I can prove|we proved|I proved|am reliable|rely on me|rely on us|be reassured|you can hold me accountable|you can hold us accountable|see with your own eyes|vote of confidence|our mission|my mission|my commitment|our commitment|during our government|during my government|while I was in charge")
finger_pointing <- stringr::str_squish("are inconsistent|is inconsistent|being inconsistent|are irresponsible|is irresponsible|being irresponsible|their fault|not my fault|not our fault|they left us with|they are responsible|are not responsible|aren’t responsible|is not responsible|isn’t responsible|costed us|false promises|lack accountability|lacking accountability|not kept their word|not kept his word|not kept her word|not kept promises|not kept the|not kept his|not kept her|not kept their|not keep their word|not keep his word|not keep her word|not keep the|didn’t keep the|didn’t keep her|didn’t keep his|hasn’t kept his|hasn’t kept her|not recognize|he made mistakes|she made mistakes|they made mistakes|not our mistake|not my mistake|not take responsibility|not my responsibility|not accountable|him accountable|them accountable|her accountable|blame them|blame him|blame his|blame her|their blame|break promises|broken promises|has betrayed|they betrayed|betraying|will betray|has tricked|has lied|not deliver|didn’t deliver|hasn’t deliver|failed your obligations|failed in your obligations|failed his obligations|failed her obligations|failed in his dut|failed in her dut|failed his dut|failed her dut|failed your dut|stabbed in the back")
origins <- stringr::str_squish("I was born|I come from|we come from|I grew up|growing up in|my parents|my mom|my mother|my father|my dad|my family|raised me|I was raised|we were raised|we grew up|my background|being surrounded by|being exposed to|my siblings|going to school in|our local church|Sunday mass|Saturday mass|family tradition|tradition in my house|in our house|growing up|back in the day|my grandparents|in my town|in my state|in my region|our community|in my community|our town|our state|my hometown|our hometown|my home state|our home state|back home|our house|my house|our neighbourhood|in my district|I lived in|we lived in|we used to play|I used to play|I was thought")
common_sense <- stringr::str_squish("is common sense|are common sense|everyone knows|it is undeniable|stating the obvious|say the obvious|everyone agrees|we all know|common wisdom|the people know|popular knowledge|from experience|it is my experience|sound judgment|practical solution|practical choice|practical answer|pragmatic solution|pragmatic answer|pragmatic choice|realistic answer|let me tell you about|is obvious|are obvious|obvious answer|obvious solution|as we all learned|we have all learned that|do not need to tell you that|the reality is|there is no logic|it does not make sense|it doesn’t make sense|we know it does not work|no one disagrees that|no person disagrees|there is not a person|there is not a human being|there is not a family|there is not an American|there is no single citizen|there is not one single person|there is not one single human being|there is not one single family|there is not one single American|there is not one single citizen|there is not one single person|there is not one human being|there is not one family|there is not one American")
anti_pc<- stringr::str_squish("politically correct|political correctness|PC|plain speaking|speaking my mind|speak my mind|say what I think|saying what I think|not going to pretend|not pretend|speak what you think|not what you want to hear|not butter up|not beat around the bush|cut to the chase|just being real|saying what everyone thinks|say what everyone is thinking|speaking plainly|coloured people|negro|retarded|nigger|third world|oriental people|crippled people|is crippled|culturally deprived|drug addict|junkie|drunk|fat people|fat person|fat population|handicapped|homosexual|faggot|deviant|perverted|illegals|illegal immigrants|illegal alien|^jew$|^jews$|non-white|prostitutes|promiscuous|stupid|tribe|underdeveloped")
territory <- stringr::str_squish("have been to|have visited|came all the way to|back from|will visit|saw first-hand|see first-hand|we visited|I visited|we visited|travelled to|traveling to|spend a few days in|spent some time in|spent time in|met great people in|we were hosted|I was hosted|our time in|my time in|our visit|spent a lot of time in|were many times in|got to know the whole country|got to know all the states")
# Get each performance as frequencies per row, the (?i) makes it case insensitive
US$truth <- stringr::str_count(US$text, paste0("(?i)", truth_telling))
US$lies <- stringr::str_count(US$text, paste0("(?i)", lie_accusations))
US$consistency <- stringr::str_count(US$text, paste0("(?i)", consistency))
US$fpoint <- stringr::str_count(US$text, paste0("(?i)", finger_pointing))
US$origins <- stringr::str_count(US$text, paste0("(?i)", origins))
US$common_sense <- stringr::str_count(US$text, paste0("(?i)", common_sense))
US$anti_PC <- stringr::str_count(US$text, paste0("(?i)", anti_pc))
US$territory <- stringr::str_count(US$text, paste0("(?i)", territory))
# Same dictionary but in Portuguese
truth_telling <- ("a verdade e|esta e a verdade|digo a verdade|dizemos a verdade|pura verdade|não e mentira|não estou mentindo|e honesto|sou honesto|somos honesto|sendo honesto|a honestidade|ser sincero|e sincero|com sinceridade|e verdade|são verdadeiras|não sou mentiroso|não minto|fundo do meu coração|sou verdadeiro|somos verdadeiros|tenho certeza|certeza absoluta|confia em mim|confie em mim|pode confiar|sou franco|somos francos|fraqueza|falando a verdade|falo a verdade|falamos a verdade|acredite em mim|pode acreditar|podem acreditar|eu tenho certeza|isso e a verdade|somos honestos|com honestidade|toda a sinceridade|com sinceridade|toda sinceridade|sou confiável|somos confiáveis|as coisas são assim|a realidade das coisas|juro por deus|com certeza|digo com precisão|veracidade|premissa|afirmo para vocês|isso e como aconteceu|falar umas verdades")
truth_telling <- stringr::str_squish(truth_telling) # removes unseen white spaces
lie_accusations <- ("não e verdade|não e verdadeiro|e mentiroso|está mentindo|são mentiroso|e mentira|de mentira|tudo mentira|e desonesto|mentiram|mentiu|um desonesto|esse desonesto|de desonesto|são desonesto|e falso|são falsos|são corruptos|e corrupto|de corrupto|todos corrupto|não são sincero|não e sincero|não são honestos|não e honesto|são trapaceiros|e trapaceiro|eles trapaceiam|trapaceou|e enganar|ser enganado|vão enganar|sendo enganados|e hipócrita|e enganador|e enganação|duas caras|enganado por|não acredite|eles finge|ele finge|e fingimento|ela finge|quebrou a sua confiança |quebra de confiança| e falso|são falsos|falsidade|e ficção|história para boi dormir|historinha para boi dormir|e calunia|são calunias|difamação|difamar|uma inverdade|são inverdades|e inverdade|isso e invenção|essas são invenções|isso e uma lenda|essas são ledas|tenta iludir|tentando iludir|uma farsa|tramoia|mal intencionado|mas intenções|falta de informação|esta mal-informado|estão mal-informados")
lie_accusations <- stringr::str_squish(lie_accusations)
consistency <- ("nós entregamos|eu entreguei|veja com seus próprios olhos|cumpro minhas palavras|cumprimos nossas palavra|cumpri minha palavra|cumpro minhas promessas|nossas promessa|um compromisso|meu compromisso|tenho um compromisso com|eu sou responsável|eu assumo a responsabilidade|nós somos responsáveis|nós assumimos a responsabilidade|nosso dever|meu dever|dou minha palavra|faço uma promessa|fazer uma promessa|aceitar a responsabilidade|aceito a responsabilidade|aceitamos a responsabilidade|aceitar a culpa|meus erros|que errei|eu errei|eu garanto|eu posso garantir|eu prometo|podemos provar|posso provar|provaremos|eu provei|voto de confiança|encarrego pessoalmente|encarreguei pessoalmente|estou comprometido|meu comprometimento|comprometimento com|o comprometimento|fazer o possível|minha supervisão|minha missão|nossa missão|no meu governo|no nosso governo|durante nosso governo|eu era encarregado|eu era o encarregado|fomos encarregados de")
consistency <- stringr::str_squish(consistency)
finger_pointing <- ("e inconsistente|são inconsistente|e irresponsável|são irresponsáveis|culpa deles|a culpa não e minha|não e minha culpa|eles nós deixaram|são responsáveis|e responsável|nós custou|falsas promessas|falta de prestação de contas|falharam|falhou|não cumpriu|não cumpriram|não reconheceu|não reconheceram|errou|erraram|não se responsabiliza|não me responsabilizo|culpa e sua|sua culpa|quebrar promessas|promessas quebradas|quebra de promessas|fala uma coisa e faz outra|fala uma coisa aqui e faz outra|falsas promessas|são trapaceiros|cometeu erros|cometeram erros|não reconhece|não reconheceu|assumiu a responsabilidade|promete uma coisa|promete o mundo|traiu a confiança|traiu a sua confiança|quebra de confiança|quebraram sua confiança|e falcatrua|foi falcatrua|cheio de falcatrua|houve fraude|houveram fraudes|fraudulento|uma negociata|facada nas costas|faltou com respeito|não faz o que promete|não fez o que promete|promessas em vão|palavras em vão|falta de comprometimento|falta de compromisso|houveram desvio|houve desvio|a culpa e do|cheio de promessas|a conta não fecha|não terminaram")
finger_pointing <- stringr::str_squish(finger_pointing)
origins <- ("Eu nasci|Eu vim de|eu venho de|viemos de|cresci|nós crescemos|meus pais|minha mãe|minha mãe|minha família|fui criado|fomos criados|minhas origens|meus irmãos|meu irmão|minha irmã|tradição familiar|tradição em casa|crescendo|antigamente|meu avô|minha avó|meus avós|na minha cidade|no meu estado|na minha região|nossa comunidade|na minha comunidade|nossa cidade|nosso estado|cidade natal|estado de origem|minha casa|nossa casa|lá em casa|nosso bairro|no meu bairro|eu morava|vivíamos|na minha terra|de onde eu venho|missa de domingo|missa toda semana|brincava|eram outros tempos|fui educado|morávamos|eu morei|nós moramos|de onde venho|eram tempos diferentes")
origins <- stringr::str_squish(origins)
common_sense <- ("senso comum|bom senso|todos sabem|afirmando o óbvio|todos concordam|todos sabemos|sabemos todos|todos nós sabemos|sabedoria popular|por experiência|e minha experiência|sou prático|tem que ser prático|devemos ser prático|sendo prático|sou pragmático|tem que ser pragmático|devemos ser  pragmático|sendo pragmático|sou realista|sendo realista|sejamos realista|realisticamente falando|e óbvio|como todos nós aprendemos|como sabemos|não preciso te dizer|o povo sabe|agente aprendeu|nós aprendemos|nós sabemos|não tem logica|como aprendemos|não faz sentido|não fazem sentido|estamos cansados de saber|sabemos que não funciona|ninguém discorda que|não tem uma pessoa|não existe uma pessoa|não há uma pessoa|não existe um ser humano|não tem um ser humano|não há um ser humano|não tem uma família|não existe uma família|não há uma família|não tem um brasileiro|não há um Brasileiro|não existe um brasileiro|não tem uma brasileira|não há uma Brasileira|não existe uma brasileira")
common_sense <- stringr::str_squish(common_sense)
anti_pc<- ("politicamente correto|falar francamente|falando francamente|falar o que penso|falo o que penso|falando o que penso|dizer o que penso|papas na língua|não vou fingir|não estou aqui para agradar|falar o que você pensa|o que você quer ouvir|não adulterar|não rodeio|não dou rodeio|direto ao ponto|dizer o que todos pensam|dizendo o que penso|dizendo o que todos pensam|dizer o que todos estão pensando|não vou amaciar|não dá para amaciar|gordos|retardado|retardada|veado|população preta|os pretos|as pretas|terceiro mundo|viciado em drogas|bêbado|drogado|sem cultura|pervertidos|promíscuo|imbecil|estupido|aleijado|defeituoso|incapacitado|inválido|mongoloide|deficiente mental|deficiência mental|o incapacitado|a incapacitada|travesti|homossexualismo")
anti_pc <- stringr::str_squish(anti_pc)
territory <- ("estive em|visitei|voltou de|voltei de|voltando de|voltamos de|estive em|estivemos em|visitará|visitarei|vi em primeira mão|ver em primeira mão|visitamos|viajei para|passei alguns dias em|passei algum tempo em|passei um tempo|conheci ótimas pessoas|conhecemos ótimas pessoas em|fomos hospedados|minha passagem|nossa passagem|nossa visita|fui muitas vezes para|estive muitas vezes em|passei muito tempo em|meu tempo em|estive por todo o Brasil|de norte a sul do pais|conheço todo o pais|conheci todo o pais|conheci todo o Brasil|conheço todo o Brasil")
territory <- stringr::str_squish(territory)
# Get each performance as frequencies per row, the (?i) makes it case insensitive
BR$truth <- stringr::str_count(BR$text, paste0("(?i)", truth_telling))
BR$lies <- stringr::str_count(BR$text, paste0("(?i)", lie_accusations))
BR$consistency <- stringr::str_count(BR$text, paste0("(?i)", consistency))
BR$fpoint <- stringr::str_count(BR$text, paste0("(?i)", finger_pointing))
BR$origins <- stringr::str_count(BR$text, paste0("(?i)", origins))
BR$common_sense <- stringr::str_count(BR$text, paste0("(?i)", common_sense))
BR$anti_PC <- stringr::str_count(BR$text, paste0("(?i)", anti_pc))
BR$territory <- stringr::str_count(BR$text, paste0("(?i)", territory))
```

\pagebreak

# 1 Introduction

In the second sentence of his inaugural speech as president of Brazil, Jair Bolsonaro declared the day in which the people began to be freed from political correctness ^[Find the whole speech here. Besides denouncing PC, Bolsonaro has also frequently referred to indigenous peoples and LGBT community in politically incorrect ways.]. Bolsonaro is not unique in this sense, other politicians as Trump, Chavez, Morales, Berlusconi, Bush, Sanders, and Lula, have openly denounced political correctness (PC) and/or publicly employed politically incorrect language ^[PC is used as an abbreviation for political correctness and politically correct. Trump denounces PC and employs politically incorrect language across several domains ranging from immigration to race and indigenous people. Trump’s 'war' on PC is frequently brought up in campaign [rallies](https://edition.cnn.com/2018/10/30/politics/donald-trump-hate-speech-anti-semitism-steve-king-kevin-mccarthy/index.html) and on [Twitter](https://www.thetrumparchive.com/?searchbox=%22politically+correct%22). Morales displays 'bad manners', favors plain speaking and is not PC often making sexist and homophobic [comments](https://www.bbc.com/news/world-latin-america-34851896). When it comes to Hugo Chavez, the leader making public sexual comments during his talk show aired on national television, towards George W. [Bush](https://www.youtube.com/watch?v=lOsABwCrn3E), among many others controversial [remarks](https://elpais.com/internacional/2013/03/06/actualidad/1362528053_830886.html). Berlusconi has numerous times made references to Barack Obama’s skin [color](https://www.theguardian.com/world/2009/sep/28/obama-tan-berlusconi) in incorrect ways, made similar comments about some football [players](https://www.si.com/soccer/2013/02/06/mario-balotelli-racism-ac-milan), and made several sexist and homophobic public [remarks](https://time.com/5179379/italy-silvio-berlusconi-sexist-remarks-women/). Lula quickly recalled the national guide on PC language as he constantly used several of the expressions listed in his speeches and campaign [rallies](https://www1.folha.uol.com.br/folha/brasil/ult96u68810.shtml). Bush, while president, famously denounced PC language on campuses during a commencement [speech](https://www.youtube.com/watch?v=4IORaF6fi_Y). Bernie Sanders stated several times how important PC was for Trump’s campaign and PC had gone too [far](https://qz.com/865263/bernie-sanders-and-political-correctness-democrats-are-learning-all-the-wrong-lessons-from-donald-trump-election-win/).]. Broad audiences appear to respond positively to these statements in multicultural countries, such as the United States (US) and Brazil, where large portions of the population fall under racial, ethnic, and other categories PC language attempts to safeguard ^[Most Americans appear unsupportive of PC language with estimations that range from 52% of the population [@montanaro2018] to 80% of the population disliking PC [@mounk2018]. This change in percentages derives from the variety of questions that are asked. For example, one poll asked if participants thought that PC was a big issue in the US, while another asked if they favored the process of the country becoming more politically correct. For Brazil, a recent national poll asked participants whether they agreed that the 'PC patrol is making the world too boring'; 56% of participants agreed completely or partially with the statement [@goncalves2020].]. Populist scholars argue that contemporary populist’s profit from breaking with PC language and use PC to identify modern elites [@mudde2004] ^[To discuss whether, or the extent which, Bolsonaro and Trump are populists is not the objective of this paper, though there are many excellent discussions on this topic [see @tamaki2020; @hawkins2018].]. Cultural backlash scholars argue that anti-PC discourses speak to resentment caused by silent liberal changes [@norris2019]. However, both populism and cultural backlash focus on specific manifestations of these discourses by specific leaders that embody their arguments, leaving aside any systematic or empirical analysis of language usage or patterns across contexts. *How, then, anti-PC discourses appear and change over time in politics?*

This paper argues that anti-PC discourses in politics are discursive performances of authenticity. Performances are the projections of a situation when one appears before others to attempt and project a definition of the situation [@goffman1956]. Perceived authenticity, as a character trait that conveys ones’ convictions, is connected to higher levels of political trust from electorates [@stiers2021; @valgarosson2021] and essential to a candidate’s political success [@alexander2010; @fordahl2018]. As an authenticity performance, anti-PC language reduces the perceived link between thinking and saying to audiences [@conway2009; @conway2017]. Still, anti-PC is not the only authenticity performance in politics. This article then develops a framework to identify various types of authenticity performances in political discourses. The framework focuses on the performative display (what), projection (who, when, and where), and mechanisms (how). Authenticity performances are divided into two types, individual and collective. Individual authenticity performances derive plausibility from audiences' expectations about a political performer, these performances include claims of truth, lie accusations, taking responsibility, or pointing fingers at other politicians. Collective authenticity performances derive plausibility from shared cultural knowledge between politicians and audiences, these include pointing at origins, allusions to common sense, anti-PC discourses, or assertions of territorial knowledge.

Political discourses at the national level in Brazil and the US since the 1980s are gathered and explored to assess variations across time, by politicians, and in different settings. The 1980s were chosen as they mark the beginning of the university debates surrounding PC language in the US, and the decade in which democracy was re-established in Brazil. Texts for campaign remarks, debates, interviews, and official speeches for presidents and presidential candidates in Brazil and the US are scraped to construct the datasets. A purpose-built dictionary of terms is created to capture various authenticity performances in discourses. The analysis indicates that the total frequencies of authenticity performances are not systematically greater in election years. Most politicians perform authenticities above the 95th percentile when they are candidates, before being elected a first time, or after having left office. However, in the case of Brazil, we see a spike in the frequency authenticity is performed in politics from 2010 to 2016, the Dilma Rousseff years. Women in politics, arguably, need to personally justify themselves and their public policy choices more frequently than the man in the sample. Moreover, the variation in types of authenticity performed in time and across cases indicate that contextual conditions make some types of performances more, or less, credible to audiences at certain junctures. In such, politicians adapt to perform authenticities audiences “want to hear”. Indeed, many authenticity performances appear in high frequencies for opposing, and associated, candidates in similar years. Finally, debates became the setting in which authenticities are performed most across cases, while interviews are the setting in which authenticity was performed least frequently, in both cases in recent years. Social media platforms give candidates diverse outlets to interact with audiences bypassing journalists in interviews, whereas debates are large-scale media events that produce “sticky” political bites charged with imagery that circulate more than ever in democracies.

# 2 From PC and Anti-PC to Populism and Backlash

## 2.1 PC and anti-PC overview and effects

Definitions of PC range from an "idealistic intervention" to "liberal fascism" [@hughes2011; @feldstein1997]. In practice, PC language avoids judgmental terms, preferring euphemistic substitution and presupposes that lexicon changes mediate discrimination in positive ways [@hughes2011, p. 13] ^[For a good discussion of lexicalization and language change in linguistics, refer to [@brinton2005]. For a discussion on the complexities involved in why language changes, and not, as well as how meaning might be affected by such changes refer to [@bybee2015]]. Anti-PC discourses, instead, represent a *dismissal of PC substitutions and/or the denouncing of PC language and users*. However, to understand what anti-PC language entails, we must first briefly overview PC’s history and effects. The modern conception of 'political correctness' originated in Mao Tsé-Tung's depiction of the 'correct socialist party line in the 1930s, used to describe "doing the right things" and "thinking the right thoughts" [@hughes2011]. The term was picked up by leftist circles in the US during the 1960s and used to describe more orthodox followers of socialism or as a critique of excessive orthodoxy [@feldstein1997; @weigel2016; @hughes2011]. It was not until the 1980s that right-leaning conservative elites in the US, including many academics, started denouncing PC language substitutions as a left leaning strategy that restricted freedoms of speech [@feldstein1997; @weigel2016]. These conservative elites were able to swiftly recycle the meaning of PC by keeping some of its' original meaning, but disconnecting it from historical context, and conflating it with enemy building narratives and imagery [@feldstein1997].

The university debates in the 1980s and 1990s brought wide attention to PC, multiculturalism, and affirmative action in the US [@berman2011]. @d1991, for example, discussed the apparent duplicity between a liberal educational system and multicultural claims, arguing that PC further victimizes minorities on campuses and undermines their merits with affirmative action policies that could potentially generate more racist backlash. As a response, Gutmann and Habermas highlighted how misplaced PC debates politicized and polarized important societal dialogues [@gutmann1994]. Yet, most multiculturalism scholars at the time dealt with PC as a matter of public or party disagreement and lamented their popularity with certain communities while leaving unaddressed the nature of PC language, the relation between the speaker's identity to the information provided, and why diverse communities related or contested these semantic changes [@loury1994]. The university debates helped disseminate and connect matters of PC, affirmative action policies, and multiculturalism to left leaning (progressive) political ideologies and anti-PC to right-wing (conservative) ideologies across the world [@feldstein1997; @bush1995]. By the mid-1990s, PC debates in the US had become as much about rhetorical strategies to forward ideological political agendas as about the diverse cultural movements' efforts to re-label [@feldstein1997; @hall1994].

The spreading of issues covered by PC language and the complex political forces supporting it, and opposing, required that the cultural and individual effects of PC in society be theorized. @hall1994, for example, describes the ambiguous truth and contested cultural authority of the PC phenomenon to argue that individuals may disapprove PC language because these are relatively new demands for cultural transformation. Similarly, @fairclough2003 (p. 24) argues that PC is a socially constructed cultural and political label for which effects depend on the resistance of structure and practices. Even though euphemistic substitutions are not a modern manifestation, as changing orthodoxies under moral imperatives exist since the invention of printing, PC language has exponentially expanded the number of substitutions [@hughes2011]. This expansion of PC language generates more abstract and imprecise replacements that can feel unnatural and create confusion, patronize subjects, and further socioeconomic inequalities via linguistic processes [@hughes2011]. This contributed to the evolution of PC from a noun used to describe language substitution to an adjective used to describe excess politeness or evasion of truths in society or for individuals [@weigel2016; @chait2015].

## 2.2 Anti-PC and populism(s)

In *The Populist Zeitgeist*, on the rise of populist parties in liberal democracies, @mudde2004 (p. 543) defines populism as a thin centered "ideology that considers society to be ultimately separated into two homogeneous and antagonistic groups, ‘the pure people’ versus the ‘corrupt elite’, and which argues that politics should be an expression of the volonté générale (general will) of the people". There are three mentions of PC in the article. They discuss how contemporary populists profit from breaking with politically correct language, because citizens' increased emancipation made issues surrounding PC more widespread, alongside how PC has been used to identify a modern elite [@mudde2004, p. 594 - 602]. Since then, populists have routinely been associated with anti-PC discourses. Still, Mudde's analysis leaves undertheorized which elites are characterized as PC by various populist leaders with a variety of ideological commitments. This is puzzling since many political, economic, and intellectual elites are often the drivers of anti-PC discourses in societies. Moreover, for @mudde2004 @mudde2007, populism is not a standalone ideology ^[See @aslanidis2016 for a good discussion on whether populism is an ideology.]. This makes it hard to pinpoint if anti-PC discourses are a portion or manifestation of the populist thin ideology, an adjacent ideology, or a contextual feature of a specific society. Besides, the account leaves unclear when, and why, anti-PC discourses are a politically profitable strategy for populists but not for other political actors. In such, there appears to be a leap associating populism with anti-PC discourses without systematically or empirically analyzing its usage in time and patterns across contexts. Other influential theories of populism do not mention anti-PC discourses [see @weyland2001; @laclau2005; @hawkins2009] and, when mentioned, anti-PC discourses fulfill a peripheral role to help identify exclusionary right-wing populist parties in Europe [@betz2001].

Recent efforts to rethink populism as a political performance or a repertoire, rather than a (thin)ideology, focus on patterns of communication in populism. For instance, @moffitt2014 (p. 387) argue that we must rethink populism as "the repertoires of performance that are used to create political relations". More specifically, we must think about how populists perform the people, threats, breakdowns and crisis, and bad manners [@moffitt2014; @moffitt2016]. Concerning bad manners, the authors argue that "much of populists' appeal comes from their disregard for 'appropriate' ways of acting in the political realm" [@moffitt2014, p. 392]. Bad manners often performed with swearing, slang words, and political incorrectness @moffitt2014, p. 392]. Performing these repertoires helps politicians appear as an "outsider" against the "establishment"[@moffitt2014; @moffitt2016]. Likewise, arguing against a minimal and pure definition of populism, @brubaker2020 (p. 60) contends that populism is a discourse and stylistic repertoire that includes 'a communicational style that claims to favor plain-speaking, common sense and authenticity against intellectualism and political correctness'. Anti-PC discourses then became a portion of a broad populist communication style or repertoire; though favoring plain speaking, displaying bad manners, or being anti-PC, are not exclusive to populists or connected to populist discourses by ideology ^[@brubaker2017 @brubaker2020 view of anti-PC discourses is not inconsistent with @mudde2004 @mudde2007 point about PC and elites. Rather it implies that certain intellectual elites might be tagged as PC, not any elite, and this is connected to anti-intellectualism. This is also consistent with @hughes2011 argument about PC language expansion that leaves some people feeling patronized and confused by PC language.].

## 2.3 Anti-PC Backlash

At the intersection between populism, authoritarianism, and multiculturalism, *Cultural Backlash* argues that authoritarian populists appeal to more conservative portions of the electorate who feel ignored seeing their societies shift towards post-materialism [@norris2019]. These factors, alongside economic fluctuations and immigration flows, allow leaders to exploit generational gaps by voicing cultural backlash and enacting reactionary policies [@norris2019, p. 446]. There are eight mentions of PC in the book. On anti-PC, the authors argue that social conservative individuals with authoritarian orientations react to some trends with feelings of resentment for the erosion of respect for their core values and that "is the essence of the backlash against 'political correctness', in which sexist language, anti-foreigner sentiments, or the expression of racist attitudes are condemned by the liberal consensus and silenced in mainstream political debate" [@norris2019, p. 123]. Rather than developing further the mechanisms of how anti-PC discourses work, deliberate on which types of anti-PC discourses connect to resentment, or exemplify what is meant by anti-PC discourses, the authors take for granted that anti-PC discourses are connected to resentment, and that is why they resonate with "old, rural, or uneducated" electorates ^[@norris2019 appear to 'passively' pass on the blame to 'old, rural, and uneducate' voters for 'undesirable' political outcomes with broad causal explanations extrapolated from thin linear correlations that illustrate little of these complex relationships. Others, as @mishra2017, rely on a misplaced engagement with history that focus on a few instances that exemplify arguments as if these were the rule.]. Nevertheless, anti-PC discourses appear to resonate more broadly within societies for various reasons, many unrelated to resentment (e.g. humor) ^[There are countless examples of PC and anti-PC language being explored humoristic ways for entertainment as, for example, notoriously, TV shows as 'South Park', 'The Office', and 'It’s Always Sunny in Philadelphia'.]. How Bolsonaro, for example, employs anti-PC in quick, direct, and short comments that focus on culturally salient themes without being necessarily internally coherent is, arguably, more decisive to his following than the content itself @carlo2018. Or how Trump is characterized as 'not PC', as a positive character trait, appears more decisive to voters than his recognizable flaws or the negative meanings associated to what he is indeed saying ^[Bill Maher, a journalist and comedian who was the host of a television series called Politically Incorrect in the 1990s, [contends](https://www.youtube.com/watch?v=CCQ3VyKe1Vs) that 'when you talk to Trump supporters, they’re not blind to his myriad flaws, but they always say he is not politically correct'.]. While both the cultural backlash and populism accounts of anti-PC in politics have merits, they focus on a few specific manifestations of these discourses by specific leaders that embody their respective arguments. Consequently, these literatures only partially explain what anti-PC discourses are, how they function, or why they matter for political outcomes.

# 3	Theory

## 3.1 Performance, authenticity, and anti-PC in politics

Performances are the projections of a situation when one appears before others, "however passive their role may seem to be, will themselves effectively project a definition of the situation by virtue of their response to the individual" [@goffman1956, p. 3]. But why should we understand discursive politics through performance or, rather, why do politicians say the things they do? Conventionally, there are two broad types of answers to this question. On the one hand, politicians might say the things they do according to what is more profitable to them (i.e. rational choice). On the other hand, politicians might say the things they do because of their beliefs (i.e. ideology). Though, neither may hold in practice as politicians can, at different times, say what is more profitable, say what they believe in, or say things without intentionally thinking about it. Usually, whether a politician is saying what they believe in, or what is more profitable, depends on the audiences’ interpretations. Alternatively, understanding politics though performance offers a more flexible answer to why politicians say the things they do, that is, to project their understandings. Performance allows to theorize that audience’s interpretation hinges on factors beyond discursive content or meaning, such as how things are said. Seeing politics through performance provides more realistic assumptions to theorizing how politicians “do politics” [see @dijk1997].  Understanding politics through performance focus less on causality and interpretation of message meaning in discourse and more on identifying discursive patterns and functioning.

Still, getting to audience’s perception and discursive elements beyond text is challenging. There are, however, several capturable discursive displays connected to the how, the where, and when of political performances that allows to identify patterns and variation in political performances. A good performer or performance, for example, is successful in projecting a view of a situation or context and connecting with audience, both of which can be connected to authenticity perceptions. Additionally, performance emphasizes the performer's role, the script, the stage, and the audience, rather than only the meanings associated with the content of a political discourse. There are also important implications of thinking discursive politics through performances. Performance places agency both with audiences, watching and evaluating politicians "doing" politics, and with political performers. This means script changes can be theorized to be intentional individual innovations or unintentional chattering by performers, while political accomplishments reflect positive evaluations from audiences. This does not mean factors such as social media, economic crisis, and cultural changes, among other factors, are irrelevant. Instead, these become political themes to be explored in politics and provide context for audiences' interpretation.

Authenticity has long been discursively performed in politics with, for example, self-references to origins, remarkable stories, allusions to civic tradition, and displays of 'vulgarism' [@fordahl2018, p. 309; @alexander2010]. Authenticity is an individualistic performance that aims at radiating truthiness outward [@taylor1992; @fordahl2018]. Authenticity in politics does not concern being truthful to oneself but appearing coherent with individual or societal values to audiences [@valgarosson2021; @fordahl2018]. @stiers2021 refer to authenticity in politics as an essential character trait that conveys candidates' convictions and that has positively affected electoral preferences across several European democracies. As a political tool, authenticity helps build political trust for candidate by demonstrating to electorates that politicians are in touch with ordinary people and their struggles [@valgarosson2021]. Authenticity perceptions were, for example, essential for Obama's success in 2008 [@alexander2010] and, arguably, defined the 2016 American election in Trump's favor [@fordahl2018]. Authenticity, in politics, is an unstable and malleable label that requires social validation; it demands contortion, modification, and active individual effort [@fordahl2018]. Therefore, authenticity, as a political performance, not always culminate in consistency, but appearing real to one’s inner self to many in audiences.

In social psychology, PC language is understood as a communication norm that attempts to remove negative language by means of self and group censorship [@conway2009; @conway2017]. This communication norm is shown to backfired due to contamination of individual information processes by authority or legitimacy effects [@conway2009; @conway2017]. Authority effects surrounding PC language occur when language is believed to be insincere if it is commanded by an authority [@conway2009]. Legitimacy effects are caused by individuals' own self-censorship, which leads to increased awareness that language interactions may not be genuine [@conway2009]. Building on these findings, @rosenblum2020 uses several survey experiments to illustrate how politically incorrect language makes political communicators appear more authentic, to have stronger convictions, and to be less strategic, in comparison to PC politicians. In fact, the denouncing of a "PC politician" or a "PC ideology" engrains an allusion to inauthenticity, to someone or something that expresses its views in calculated ways to avoid judgment [@hughes2011; @weigel2016]. Anti-PC discourses are connected to authenticity in politics by reducing the perceived link between thinking and saying for audiences [@conway2017] ^[The argument also considers the insights of `bad manners` as a repertoire [@moffitt2016; @moffitt2014] of `plain speaking` as communication style [@brubaker2017; @brubaker2017] in populism. Though the conceptualization here is broader and intends to theorize anti-PC outside of populism, it is somewhat consistent with how these theorists understand what these repertoires/styles are, how they work in politics, and why they matter.]. Hence, anti-PC performances signals to audiences’ precisely that politicians might be authentic to inner self. Though, as alluded above, anti-PC is one authenticity performance and authenticity in politics can be performed in politics in a variety of ways.

## 3.2 Authenticity performances

@valgarosson2021 argue that there are three broad types of authenticities, historic, categorical, and value: value authenticity (i.e. the authentic politician) being the most pertinent in politics. @stiers2021 connect authenticity in politics to a sense of “realness” that, in recent times, has repeatedly turned to anti-politics to connect politicians to ordinary people. But how authenticity as this abstract attributed individual trait or group perception, with huge political implications, come about in politics? Looking at authenticity in politics, as a performance, requires we identify displays, projections, and mechanisms. Display refers to detecting certain performance (what) and is constrained by projection and mechanism. Projection relates to the level at which it is convincing that performance is authentic. Projection encapsulates the role (who), the setting (where), and the structure (when) for certain display(s). The role relates to the part performer takes in politics. Roles can generate different expectations and ranges of possibilities for authenticity performances (e.g. candidates versus elected officials). Setting refers to where a performance takes place (e.g. debate or official speech). Structure indicates the timing in which performance is inserted (e.g. before/after an election). Mechanisms refer to the theorized pathways (how) by which a projected display might work to produce authenticity. Diverse answers to each of these performative aspects generate different expectations about authenticity performances in politics.

Although what can be an authenticity performance, and not, is not always straight or capturable discursively, there are several indications of how authenticity has been performed in politics. @alexander2010, for example, discusses how allusions to origins, territory, and traditions were employed by Obama to connect with audiences and generate a sense of authenticity. These performances focus on the cultural connections shared by politicians and audiences and can be essential to legitimize a candidate’s knowledge about the “real” issues a country face. @fordahl2018 argues that Trump’s authenticity built upon iconic, often vulgar, representations of civic life and objective reality as a “straight shooter deal maker”. Allusions to family values and his business experience were central to Trump’s performances. These noticeable types of performances in discursive politics become, then, displays of authenticity performance. Displays for authenticity performances can be divided in two broad types in political discourses: individual and collective. The types refer to the mechanism that might give plausibility to a certain performance. Individual authenticity performances derive plausibility for performance based on audiences' expectations about a political performer (or opponent) considering the information they have. These performances include stating to be telling the truth or claiming others are lying and taking responsibility for actions or pointing fingers at other's errors. Collective authenticity performances are more elaborate displays of authenticity that derive plausibility for performance based on the cultural connections shared between audiences and performer. These performances include anti-PC, pointing at origins, allusions to common sense, or claims of territorial knowledge ^[Politically incorrect expressions coded were selected from a 1992 dictionary of politically correct language, this assumes that most of these terms have for long been agreed upon as not PC [@beard1993].]. Table 1, below, summarizes each authenticity performance theorized, their respective displays, and mechanisms.

````{=tex}
\begin{landscape}

```{r Table 1, fig.cap="Authenticity Performances, Displays, and Mechanisms", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}

table1 <- tibble::tibble("Authenticity Performance" = c("Truth Telling", "Lying Accusing", "Consistency ", "Finger Pointing", "Origins", "Common Sense", "Territory", "Anti-PC"),
"Displays" = c("Mentions truthiness, sincerity, and honesty when describing oneself. Examples: 'the truth is', 'this is the truth', 'am not lying', 'is/are/am honest', 'honesty', 'is/are/am sincere', 'is/are true'", "Mentions dishonesty, untruthfulness, and insincerity when used to describe others. Examples: 'not the truth', 'not true', 'untruthful', 'is/are lying', 'is/are liars', 'is/are dishonest', 'is/are fake', 'is/are a hypocrite'", "Mentions career consistency, responsibility, accountability for individual. Examples: 'I/we delivered', 'check and see', 'keep my word', 'kept my word', 'keep promises', 'I am/we are responsible', 'I/we take responsibility', 'I/we guarantee'",
"Mentions lack of accountability, inconsistency and/or blame others for mistakes. Examples: 'are/is inconsistent', 'are/is irresponsible', 'their fault', 'not my fault', 'they left us with', 'are/is responsible', 'costed us', 'false/fake/broken promises'", "Alludes to birthplace, origins, and roots to describe background, values, and tell their story. Examples: 'I was born in', 'I come from', 'I/we grew up in', 'my family', 'I was raised', 'my background', 'I was thought', 'my hometown/community/city'", "Alludes to common sense, reason, and logic to describe choices or preferences. Examples: 'is/are common sense', 'everyone/everybody knows', 'it is undeniable', 'stating the obvious', 'everyone agrees', 'we all know', 'no one disagrees that', 'we have all learned that'",
"Alludes to sub-portions of the territory known and/or visited. Examples: 'have seen in', 'have been to', 'I/we/have visited', 'came all the way to', 'came/came back from', 'saw/see first-hand in', 'I/we were hosted', 'my/our time in'", "Alludes to PC language negatively, employs politically incorrect language, or claims to speak what one thinks without filters. Examples: 'not politically correct', 'political correctness', 'speak/speaking my mind', 'say/saying what everyone thinks', 'non-white/colored/oriental/fat/handicapped people'"),
Mechanism = c("Speaker appears to be telling the truth regarding beliefs or facts.", "Speaker appears more sincere vis-a-vis others.", "Speaker appears consistent regarding pledges.", "Speaker appears accountable for actions.", "Speaker seems culturally connected to the country.", "Speaker seems to make choices consistent with what others in society would.", "Speaker seems territorially connected to sub-regions, nation, or territory.", "Speaker seems to be saying what thinks on culturally contested themes."))

kbl(table1, booktabs = T, caption = "Authenticity Performances, Displays, and Mechanisms") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 11, full_width = TRUE) %>% column_spec(1, width="2cm", bold=TRUE) %>% column_spec(2, width="12cm") %>% column_spec(3, width = "6cm")
```

\end{landscape}
````

# 4 Methodology

## 4.1 Case selection

In Brazil, restrictions to freedoms of speech regarding racism, criminalized in the constitution of 1988, and affirmative action policies in universities, put in place since the late 1990s, were widely discussed albeit a long history of direct and indirect political opposition to these (see Freitas and Castro 2004; 2013). However, neither constitutional nor affirmative action debates sparked much discussion about PC. In effect, the PC terminology was translated from outside the Brazil (see Possenti 1995) and it did not directly appear in public-political debates until 2004, when the Secretariat of Human Rights of the President published a manual of PC language which contained 96 popular expressions deemed incorrect for being racist, sexist, or homophobic (Fiorin 2008; Morato and Bentes 2017). A that time, the federal government quickly recalled the publication due to criticism (Ibid.). Since the mid-2000s humoristic interpretations of politically incorrect language and politically charged calls against a PC country started to appear frequently in the media (Morato and Bentes 2017; Weinmann and Calau 2014). Alongside this, several articles in popular periodicals such as magazines and newspapers, as well as some influential books, have been written opposing PC language ever since (Weinmann and Calau 2014). By the 2010s, PC in Brazil started to be referred to as a "controversy" and, nowadays, PC in Brazil is a widely contested phenomenon in society and politics.

Nonetheless, Brazil and the US held the two largest slave populations in the world until slavery was abolished in each country respectively. Similarly, these two countries became large settler states for diverse groups of migrants in the following centuries. These historical processes rendered their current populations heterogenous in terms of demographic composition and cultural heritage. Such makes PC language's appearance and influence in these societies understandable, but the eminence of anti-PC discourses in national politics is somewhat puzzling as electorates are likely to encompass several large groups PC language safeguards. While Brazil and the US are relatively similar in geographical and population sizes, they are dissimilar in many other ways as levels of economic development, culture and, in some ways, their political systems. Thus, each case is understood as configuration, formed by the aggregation of parts that make sense in the context of the case (Ragin 1987). This allows us to consider similarities and differences across time and space and broadly compare them in many aspects, including political discourses.

## 4.2 Data

Text data on official speeches, campaign rallies, debates, and interviews for elected presidents and runoff candidates were gathered since 1980 for the US and 1985 for Brazil. The 1980s marked the beginning of the university debates surrounding PC in the US. In Brazil, democracy came back in 1985, though direct presidential elections were held in 1989. All the text for the US were scrapped from (The American Presidency Project)[https://www.presidency.ucsb.edu] (TAPP) repository. Conversely, collecting data for Brazil proved more difficult due to availability. For official speeches, @cezar2021 dataset on official speeches for Brazilian presidents from 1985 to 2019 was updated to include the missing speeches from 2019 to 2021 using the (Brazilian Presidential Library)[http://www.biblioteca.presidencia.gov.br/sobre-a-biblioteca/biblioteca-da-presidencia-da-republica]. Text for debates, interviews, and campaign rallies were scraped from subtitles automatically generated for YouTube videos. The number of videos available for later election cycles, after the 2000s, is considerably larger than earlier ones. As well, some election cycles in Brazil were shorter than others as national elections were decided on the first round, therefore, data for those cycles is more limited. For those reasons, and due to the longer time scope, the number of observations in the text datasets for the US is greater than for Brazil ^[For all the data, scripts, and additional information please request access to the authenticity performances repository available on GitHub. For more information on some the functions developed, see the poldis [@sposito2021] R package.].

The comparison of data for different settings in which politics gets done provide more complete picture of how discursive politics change, and not, in each of these settings, across time, or by politicians. Table 2, below, summarizes the number of text observations by setting in each case, the earliest date, the latest date, and the sources. For interviews, those occurring in the period between two years before elections and one year after the election (or tenure for elected) were compiled. For debates, data on runoff debates in the case of Brazil and debates after party candidates were nominated in the case of the US were gathered ^[Those are debates after party nominations in the US and runoff debates for Brazil. There are a few exceptions to this in Brazil for elections decided in the first round (e.g. 1994) or elections where candidates were unable to participate in runoff debates (e.g. 2018). In these cases, the participations of the two most voted candidates in the first-round debates were gathered. The number of debates for both Brazil and the US in Table 2 reflect the number of politicians coded for each runoff debate in dataset. That is, the text of each debate was separated by politicians.]. Campaign remarks occurring on election years for runner-up candidates were gathered. Therefore, the datasets for campaign and debates have their latest date as the last election year in each case, that is 2018 for Brazil and 2020 for the US.

```{r table 2, fig.cap="Table 2 - Text Data for Brazil and the US", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
table2 <- tibble::tibble("Country" = c("US", "US", "US", "US",
                                       "Brazil", "Brazil", "Brazil", "Brazil"),
                         "Setting" = c("Speeches", "Campaign", "Debates", "Interviews",
                                       "Speeches", "Campaign", "Interviews", "Debates"),
                         "Observations" = c(15016, 1563, 59, 936, 6130, 175, 262, 29),
                         "Earliest Date" = c(1981, 1980, 1980, 1980, 1985, 1989, 1987,1989),
                         "Latest Date" = c(2021, 2020, 2020, 2021, 2021, 2018, 2021, 2018),
                         "Source" = c("TAPP", "TAPP", "TAPP", "TAPP",
                                      "Cezar (2020)", "YouTube", "YouTube", "YouTube"))
kbl(table2, booktabs = T, caption = "Text Data for Brazil and the US") %>%
  kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),
                position= "center", font_size = 10) %>%
  column_spec(1, width="3cm", bold=TRUE) %>%
  column_spec(2, width="3cm") %>%
  column_spec(3, width = "3cm") %>%
  column_spec(4, width = "3cm") %>%
  column_spec(5, width = "3cm") %>%
  column_spec(6, width = "3cm")
```

## 4.3 Operationalization

After collection, the data was cleaned by standardizing variables across datasets and removing punctuations and accents to facilitate comparison. The texts were aggregated by politician and year. Authenticity performance, including anti-PC discourses, were identified via a purpose-built dictionary of terms that codes the discursive displays associated with each performance (see Appendix 1) ^[See also @kentikelenis2021 for a good example of a purpose-built dictionary in a bag of words approach to text analysis.]. The dictionary of terms was developed listening to samples of randomly selected speeches, campaign remarks, interviews, and debates from the datasets. The dictionary has similar definitions in Portuguese and English in relation to the words and expressions searched. The number of words included in the dictionary for each performance is similar across languages. The dictionary was designed to reduce the possibility of overlap, even as some authenticity performances might share similar displays. Directionality in the text is important to identify authenticity performances, specially to distinct when speakers talk about themselves or others, thus, no stop words were removed from the text datasets. That is, the dictionary of terms includes combinations of pronouns/determiners and verbs/nouns to avoid false-positive matches. All frequencies of authenticities performances are normalized for the number of characters in each text. Normalization helps account for discrepancies in the number of observations for the two cases and in time for the same case.

# 5 Analysis

## 5.1 Authenticity Performances in Time in Brazil and the US

On average, allusion to origins and mentions of truth telling are the two most regularly performed authenticities in Brazil and the US. Table 3, below, displays the average values for each authenticity performance by country represent, the values were normalized by the number of characters in texts. For both cases, the US and Brazil, origins and truth-telling are the two most performed authenticities on average. While origins are a collective authenticity performance (i.e. based on the cultural connections shared between audiences and performer), truth-telling is an individual authenticity performance (i.e. based on audiences' expectations about a political performer or performance). Yet, as authenticity performances, claiming to be telling the true, or being truthful, and allusions to origins promote oneself instead of focusing on others. Indeed, authenticity performance that focus on others, such as lie-accusations and finger-pointing, are performed relatively infrequently on average in both cases. Consistency, an inward-looking individual authenticity performance, also appears relatively frequently in both cases. In the case of the US, specifically, territory and anti-PC are moderately performed on average. In the case of Brazil, common sense is performed, on average, relatively frequently. Unsurprisingly, politicians appear to speak mostly about themselves when doing politics.

```{r table 3, fig.cap="Table 3 - Average Authenticity Performances in Brazil and the US", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
aut_perf_time <- US %>%
  select(-c(doc_id, setting, settingc, text)) %>%
  group_by(date) %>%
  summarise(across(everything(), sum)) %>%
  mutate(truth_telling = (truth/length)*1000,
         lie_accusations = (lies/length)*1000,
         consistency = (consistency/length)*1000,
         finger_pointing = (fpoint/length)*1000,
         origins = (origins/length)*1000,
         common_sense = (common_sense/length)*1000,
         anti_pc = (anti_PC/length)*1000,
         territory = (territory/length)*1000) %>%
  select(-c(length, truth, lies, fpoint,anti_PC))
aut_perf_time_BR <- BR %>%
  select(-c(doc_id, setting, text, settingc)) %>%
  group_by(date) %>%
  summarise(across(everything(), sum)) %>%
  mutate(truth_telling = (truth/length)*1000,
         lie_accusations = (lies/length)*1000,
         consistency = (consistency/length)*1000,
         finger_pointing = (fpoint/length)*1000,
         origins = (origins/length)*1000,
         common_sense = (common_sense/length)*1000,
         anti_pc = (anti_PC/length)*1000,
         territory = (territory/length)*1000) %>%
  select(-c(length, truth, lies, fpoint,anti_PC))
# Get means
BR_mean <- apply(aut_perf_time_BR, 2, function(x) mean(as.numeric(x)))
US_mean <- apply(aut_perf_time, 2, function(x) mean(as.numeric(x)))
# Table
table3 <- tibble::tibble("Authenticity Performance" = c("Truth Telling", "Lying Accusing",
                                                        "Consistency ", "Finger Pointing", "Origins",
                                                        "Common Sense", "Territorial", "Anti-PC"),
                         "Average US" = c(0.060483991, 0.007856627, 0.034993192, 0.003480440, 
                                          0.061912083, 0.011710489, 0.017553560, 0.016926722),
                         "Average Brazil" = c(0.059384601, 0.005166693, 0.034818219, 0.009690228, 
                                              0.144611084, 0.042071623, 0.009345240, 0.004811932))
kbl(table3, booktabs = T, caption = "Average Authenticity Performances in Brazil and the US") %>%
  kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),
                position= "center", font_size = 10) %>%
  column_spec(1, width="3cm", bold=TRUE) %>%
  column_spec(2, width="3cm") %>%
  column_spec(3, width = "3cm")
```

Authenticity performances are not monolithic in time. How, then, do their frequencies change in time? Figure 1, below, illustrates the total frequencies for authenticity performances in Brazil and the US in time. In the figure, the x-axis represents the years and the y-axis represents the sum of all normalized authenticity performances for that year. For each case, the black dots represent election years. Remarkably, the figure appears to show no systematic increases in the total frequency scores associated to election years in Brazil and the US in time ^[A linear regression that correlates election years, as factors, to the total of authenticity performances for each case has also been run. The coefficients show that for both cases the relationship between election years and the frequency of authenticity performances is slightly negative (i.e. elections year correlate with a decrease in the total of authenticity performances). This relationship is negative and statistically significant for the case of the US.]. This is puzzling considering that appearing authentic to electorates is shown to influence election outcomes [@fordahl2018; @stiers2021; @valgarosson2021]. These findings might indicate that elected politicians have more freedom to perform authenticity, or discuss less relevant policy matters, in non-election years. As well, incumbents can be more careful towards when, where, and how authenticity is performed around election years. 

```{r Figure 1, fig.cap="Total Authenticity Performances in Time in Brazil and the US", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
# Plot in time
aut_perf_time_long <- aut_perf_time %>%
  tidyr::pivot_longer(consistency:anti_pc, "Performance")
aut_perf_time_long_BR <- aut_perf_time_BR %>%
  tidyr::pivot_longer(consistency:anti_pc, "Performance")
BR_ap_total <- aut_perf_time_long_BR %>% 
  select(-c(Performance)) %>%
  group_by(date) %>% 
  summarise(across(everything(), sum)) %>% 
  mutate(Country = "Brazil")
US_ap_total <- aut_perf_time_long %>% 
  select(-c(Performance)) %>%
  group_by(date) %>% 
  summarise(across(everything(), sum)) %>% 
  mutate(Country = "US")
ap_total_time <- dplyr::full_join(US_ap_total, BR_ap_total) %>% 
  mutate(date2 = stringr::str_extract(date, "[0-9]{2}$"))
# Create labels for election years only
ap_total_time$ey <- ifelse(ap_total_time$Country == "US" &
                             grepl("1980|1984|1988|1992|1996|2000|2004|2008|2012|2016|2020",
                                   ap_total_time$date),
                           ap_total_time$date, "")
ap_total_time$ey <- ifelse(ap_total_time$Country == "Brazil" &
                             grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                   ap_total_time$date),
                           ap_total_time$date, ap_total_time$ey)
ap_total_time$ey <- ifelse(ap_total_time$ey != "", "EY", "")
# # let just check that there is not a statistically significant correlation between EY and total AP
# check_ey <- lm(value ~ as.factor(ifelse(ey == "EY", 1, 0)) + as.factor(country), ap_total_time)
# check_ey_table <- stargazer::stargazer(check_ey, type = "text")
# # Not statistically significant.. not even a positive relationship for either case.
# # In comparison to Brazil, EY in the US shows to be negative and statistically significant.
# # Let's also check if the increases per year in Brazil are statistically significant
# ap_total_time_br <- ap_total_time %>% dplyr::filter(country == "Brazil")
# check_year_br <- lm(value ~ as.factor(date), ap_total_time)
# check_year_br_table <- stargazer::stargazer(check_year_br, type = "text")
# # some Dilma years are statistically significant
ggplot(ap_total_time, aes(x = reorder(date2, as.numeric(date)),
                          y = value, fill = Country)) +
  geom_line(aes(group = Country, color = Country)) +
  geom_point(data = filter(ap_total_time, ey != "")) +
  labs(x = "",
       y = "",
       title = "Total Authenticity Performances\nin Brazil and the US in Time",
       subtitle = "Normalized by number of characters per year in dataset",
       caption = "Black dots mark election years in respective country") +
  theme_fivethirtyeight()
```

In the case of Brazil, we also see a large increase in frequencies of authenticities performed between 2010 and 2016, the Dilma Rousseff years ^[A linear regression correlating the total of authenticity performances to years, as factors, in Brazil confirms statistically significant increases for the years of 2012 and 2015, non-election years and when Rousseff was president.]. This could indicate that there is a relationship between gender and the frequencies in which authenticity is performed in politics. While there only two women politicians in the data (Rousseff and Hillary Clinton), and this makes challenging to extrapolate about how gender and authenticity performances correlate, there is a vast literature that investigate differences communication styles by gender in politics [@wood1994; @christine2005; @blankenship1995; @franceschet2016]. Rousseff, arguably, needed to justify herself and her public policies with further concrete reasoning and perform certain authenticities to connect with audiences more frequently than the man in the sample. Nevertheless, authenticity has generally been performed with greater frequency in politics in Brazil since the mid-1990s in comparison to the US, which could be related to the differences in the number of parties in the political system. Brazil has many parties and, thus, politicians are less susceptible to broad party pressure to conform and represent heterogenous interests of groups within in comparison the US with two major parties.

Though, how do the types of authenticity performed in politics change in time? Figure 2, below, illustrates how collective and individual authenticity performances change in time for Brazil and the US. In the figure, the x-axis represents the years and the y-axis represents the sum individual and collective authenticity performances for that year. In Brazil, collective authenticity performances were performed much more frequently than individual performances from the 1980s until the early-2010s. This trend begins to change at that point and, by 2019, we see a reversal of this pattern, whereas individual authenticity performance surpasses collective performances. Conversely, in the case of the US, individual authenticity performances were performed more frequently from through the 1980s. Though, from the early-1990s until the early-2010s, both performances appear at very similar rates. This pattern changes in the mid-2010s with collective authenticity performances surpassing individual. 

```{r Figure 2, fig.cap="Collective versus Individual Authenticity Performances in Time in Brazil and the US", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
aut_perf_type <- aut_perf_time %>%
  tidyr::pivot_longer(consistency:anti_pc) %>% 
  mutate(Type = ifelse(grepl("territory|anti_pc|origins|common_sense", name),
                       "Collective", "Individual")) %>% 
  group_by(Type, date) %>%
  summarise(value = sum(value)) %>% 
  mutate(date2 = stringr::str_extract(date, "[0-9]{2}$"),
         country = "US")
aut_perf_type_BR <- aut_perf_time_BR %>%
  tidyr::pivot_longer(consistency:anti_pc) %>% 
  mutate(Type = ifelse(grepl("territory|anti_pc|origins|common_sense", name),
                       "Collective", "Individual")) %>%
  group_by(Type, date) %>%
  summarise(value = sum(value)) %>% 
  mutate(date2 = stringr::str_extract(date, "[0-9]{2}$"),
         country = "Brazil")
ap_aut_perf_type <- rbind(aut_perf_type, aut_perf_type_BR)
ggplot(ap_aut_perf_type, aes(x = reorder(date2, as.numeric(date)),
                             y = value, color = Type)) +
  geom_smooth(aes(group = Type)) +
  facet_wrap(facets = "country", nrow = 2) +
  labs(x = "Year",
       y = "Normalized Value",
       title = "Collective versus Individual Authenticity Performances\nin Brazil and the US in Time",
       subtitle = "Normalized by number of characters per year in dataset",
       caption = "Curves in the plot are smoothed using loess method.") +
  theme_fivethirtyeight()
```

These diverse patterns are related to contextual conditions that make some types of performances more, or less, credible to audiences in each case in time. Audiences in Brazil likely became tired of collective authenticity performances that focus on share cultural links with the politico-economic crisis of the mid-2010s and, in turn, became more interested in simpler individual performances that are credible based on expectations for political performers. Whereas, in the US, audiences likely grew tired of performances that were balanced and focus on both collective and individual authenticities equally around the early-2010s in favor performers and performances that focus further on established cultural connections. Interestingly, in both cases, these patterns begin to change before recent election years (e.g. 2016 for the US and 2018 for Brazil) and continue after, even as politicians at the top might have changed. This indicates that timing could favor certain candidates who already perform certain authenticities, but also that politicians perform authenticities that audiences want to hear (i.e. are more credible at certain juncture).

## Authenticity Performances by Politicians in Brazil and the US

Distinct presidents and presidential candidates might focus on some authenticity performances over others. Figure 3, below, captures authenticity performances by presidents and presidential candidates that fall above the 95th percentile for Brazil and the US at a certain year. In the figure, the x-axis represents the years and the points represents a politician that performed one, or more, authenticity above the 95th percentile at that year. The 95th percentiles are calculated for each authenticity performance and for the total of authenticity performances. While some politicians and years appear multiple times, other candidates and years do not appear at all. Most politicians in Brazil and the US perform one, or more, authenticity above the 95th percentile when they were candidates, before being elected the first time (e.g. Lula), or after having left office (e.g. Clinton). This further indicates that politicians running for re-election perform authenticity less around election years. Other politicians do not perform any authenticity at the 95th percentile for any year campaigning or in office (e.g. Reagan and Cardoso). This could indicate that these politicians perform authenticity less than others or, at least, that they do not focus on one authenticity more than other politicians at any point in time.

```{r Figure 3, fig.cap="95th Percentile Authenticity Performances by Politicians in Brazil and the US", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
# First, let's fix some names
BR$doc_id <- gsub("Dilma", "Rousseff", BR$doc_id)
BR$doc_id <- gsub("Aecio", "Neves", BR$doc_id)
BR$doc_id <- gsub("FHC", "Cardoso", BR$doc_id)
US$doc_id <- stringr::str_trim(US$doc_id )
US$doc_id <- gsub("Albert Gore, Jr.", "Gore", US$doc_id)
US$doc_id <- gsub("Hillary Clinton", "H. Clinton", US$doc_id )
US$doc_id <- gsub("George W. Bush", "W. Bush", US$doc_id )
US$doc_id <- stringr::word(US$doc_id , -1)
# BR
table_ap_BR <- BR %>% 
  select(-c(text, setting, settingc, date)) %>%
  group_by(doc_id) %>%
  summarise(across(everything(), sum)) %>%
  mutate(truth_telling = (truth/length)*1000,
         lie_accusations = (lies/length)*1000,
         consistency = (consistency/length)*1000,
         finger_pointing = (fpoint/length)*1000,
         origins = (origins/length)*1000,
         common_sense = (common_sense/length)*1000,
         anti_pc = (anti_PC/length)*1000,
         territory = (territory/length)*1000) %>%
  select(-c(truth, lies, fpoint, anti_PC, length))
total <- table_ap_BR %>% select(-doc_id) %>% mutate(total = rowSums(.)) %>% select(total)
table_ap_BR <- cbind(table_ap_BR, total)
table_ap_BR <- table_ap_BR %>% 
  mutate(date = stringr::str_extract(doc_id, "[0-9]{4}$"),
         politician = stringr::str_remove(doc_id, "_[0-9]{4}$")) %>%
  arrange(date) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate('Consistency' = ifelse(consistency > quantile(consistency, 0.95), consistency, NA),
         'Origins' = ifelse(origins > quantile(origins, 0.95), origins, NA),
         'Truth Telling' = ifelse(truth_telling > quantile(truth_telling, 0.95), truth_telling, NA),
         'Lie Accusations' = ifelse(lie_accusations > quantile(lie_accusations, 0.95),
                                  lie_accusations, NA),
         'Finger Pointing' = ifelse(finger_pointing > quantile(finger_pointing, 0.95),
                                  finger_pointing, NA),
         'Common Sense' = ifelse(common_sense > quantile(common_sense, 0.95), common_sense, NA),
         'Anti-PC' = ifelse(anti_pc > quantile(anti_pc, 0.95), anti_pc, NA),
         'Territorial' = ifelse(territory > quantile(territory, 0.95), territory, NA),
         'Total' = ifelse(total > quantile(total, 0.95), total, NA)) %>%
  relocate(politician, date, 'Truth Telling', 'Lie Accusations', Consistency,
           'Finger Pointing', 'Common Sense', Origins, Territorial, 'Anti-PC', Total) %>% 
  mutate(abc = paste0('Truth Telling', 'Lie Accusations', Consistency, 'Finger Pointing',
                      'Common Sense', Origins, Territorial, 'Anti-PC', Total)) %>%  
  filter(abc != "NANANANANANANANANA") %>% 
    select(-c(abc, doc_id, truth_telling, lie_accusations, consistency, finger_pointing,
            origins, common_sense, anti_pc, territory, total)) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  mutate(country = "Brazil")
# US
table_ap_US <- US %>% 
  select(-c(text, setting, settingc, date)) %>%
  group_by(doc_id) %>%
  summarise(across(everything(), sum)) %>%
  mutate(truth_telling = (truth/length)*1000,
         lie_accusations = (lies/length)*1000,
         consistency = (consistency/length)*1000,
         finger_pointing = (fpoint/length)*1000,
         origins = (origins/length)*1000,
         common_sense = (common_sense/length)*1000,
         anti_pc = (anti_PC/length)*1000,
         territory = (territory/length)*1000) %>%
  select(-c(truth, lies, fpoint, anti_PC, length))
total <- table_ap_US %>% select(-doc_id) %>% mutate(total = rowSums(.)) %>% select(total)
table_ap_US <- cbind(table_ap_US, total)
table_ap_US <- table_ap_US %>% 
  mutate(date = stringr::str_extract(doc_id, "[0-9]{4}$"),
         politician = stringr::str_remove(doc_id, "_[0-9]{4}$")) %>%
  arrange(date) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate('Consistency' = ifelse(consistency > quantile(consistency, 0.95), consistency, NA),
         'Origins' = ifelse(origins > quantile(origins, 0.95), origins, NA),
         'Truth Telling' = ifelse(truth_telling > quantile(truth_telling, 0.95), truth_telling, NA),
         'Lie Accusations' = ifelse(lie_accusations > quantile(lie_accusations, 0.95),
                                  lie_accusations, NA),
         'Finger Pointing' = ifelse(finger_pointing > quantile(finger_pointing, 0.95),
                                  finger_pointing, NA),
         'Common Sense' = ifelse(common_sense > quantile(common_sense, 0.95), common_sense, NA),
         'Anti-PC' = ifelse(anti_pc > quantile(anti_pc, 0.95), anti_pc, NA),
         'Territorial' = ifelse(territory > quantile(territory, 0.95), territory, NA),
         'Total' = ifelse(total > quantile(total, 0.95), total, NA)) %>%
  relocate(politician, date, 'Truth Telling', 'Lie Accusations', Consistency,
           'Finger Pointing', 'Common Sense', Origins, Territorial, 'Anti-PC', Total) %>% 
  mutate(abc = paste0('Truth Telling', 'Lie Accusations', Consistency, 'Finger Pointing',
                      'Common Sense', Origins, Territorial, 'Anti-PC', Total)) %>% 
  filter(abc != "NANANANANANANANANA") %>% 
  select(-c(abc, doc_id, truth_telling, lie_accusations, consistency, finger_pointing,
            origins, common_sense, anti_pc, territory, total)) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  mutate(country = "US")
table_95_ap <- rbind(table_ap_US, table_ap_BR) %>% 
  mutate(date2 = stringr::str_extract(date, "[0-9]{2}$")) %>% 
  pivot_longer('Truth Telling':Total, "Performance") %>%
  mutate(Performance = factor(Performance, levels = c('Truth Telling', 'Lie Accusations',
                                                      'Consistency', 'Finger Pointing',
                                                      'Common Sense', 'Origins',
                                                      'Territorial', 'Anti-PC', 'Total'))) %>% 
  filter(value != 0)
ggplot(table_95_ap, aes(x = reorder(date2, as.numeric(date)),
                        y = value, fill = Performance,
                        label = politician)) +
  geom_point(aes(color = Performance), size = 3) +
  geom_text(aes(label = politician), size = 3, vjust = 1) +
  facet_wrap(facets = "country", nrow = 2) +
  labs(x = "Year",
       y = "Normalized Values",
       title = "Authenticity Performances above the 95th Percentile\nby Politicians in Time for Brazil and the US",
       subtitle = "Normalized by number of characters per year in dataset") +
  theme_fivethirtyeight()
```

When it comes to the total of authenticity performances, Mondale, Clinton, Gore, Obama, and H. Clinton perform the total of authenticity performances above the 95th percentile certain year in the case of the US, but none of these politicians were in the oval office when they did so. In the case of Brazil, Lula, Collor, Neves, and Rousseff performed the total of authenticities above the 95th percentile for a certain year. Rousseff is the only politician in the whole sample to perform the total of authenticities above the 95th percentile while in office. Interestingly, @wood1994 (p. 137-148) argues that women’s speech style in politics include personal disclosures of details, using of anecdotes, and concrete reasoning, which are consistent with common sense and origins performances that were performed above the 95th percentile by Rousseff during her years in office. The fact that Dilma performs various authenticities the 95th percentile while in office further indicates not only women in politics have a distinct style, but also that they likely feel the need perform authenticity at a higher rate to connect to audiences and justify policy choices more than their male counterparts.

When it comes to specific performances, truth telling was performed above the 95th percentile by politicians as Kerry and McCain around the year 2000, and by Obama and Sanders around the year 2020. Consistency was performed above the 95th percentile by several candidates across time, most notably Carter, W. Bush, and Clinton; and common sense was performed above the 95th percentile by Clinton, W. Bush, and Obama after they left office. In the case of anti-PC, Mondale in the 1980s and Trump in the mid-2010s perform anti-PC. Though these politicians belonged to different parties and had diverse political stands, both often employ “telling like it is” communication style ^[For more on Modale’s “truth” telling style see his (1984)[https://www.nytimes.com/1984/07/20/us/transcript-of-mondale-address-accepting-party-nomination.html] Democratic Convention acceptance speech. Some of Mondale’s mentions of truth telling regarding raising taxes, for example, is similar to numerous accounts of Trump’s denouncing PC in terms of wasting peoples time by not “telling how it is” what they might “not” want to hear.]. Comparably, for Brazil, truth telling, origins, and territory were performed above the 95th percentile by Lula and Collor in through the 1990s. In fact, Lula and Collor performed more authenticities above the 95th percentile than all other politicians during this period. When it comes to anti-PC, Sarney, Franco, and Collor stand out for Brazil in the early-1990s. Bolsonaro only performs territorial authenticity above the 95th percentile in 2019.  Particularly, the plot seems to indicate that similar authenticity performances above the 95th percentile, occur for associated and opposing politicians in similar years. This could be due to politicians responding to each other on specific authenticity performances, imitating each other at a certain election cycle, or connected to a contextual condition that make certain authenticity performance more credible around certain time.

## 5.3 Authenticity Performances across settings in Brazil and the US

The frequency of authenticity performances can also change across settings in which politics gets done ^[The relationship between the average frequencies of authenticity performances per year and setting was also investigated employing fixed-effects linear panel models. Fixed-effects models account for time effects while controlling for unobserved associations within the model variables [@allison2009]. In the regression (see appendix 2), the correlation between the frequencies of authenticity performances and campaign settings for the US, in comparison to official speeches (reference category), is positive and highly statistically significant. Interviews also appear to correlate positively with authenticity performances in the US, in comparison to official speeches. In the case of Brazil, both campaign and debate settings correlate positively with authenticity performances in relation to official speeches. However, using this approach, we miss how these correlations change in time.].Figure 4, below, illustrates authenticity performances in Brazil and the US in time and across setting. The x-axis represents the years and the y-axis represents the sum of all normalized authenticity performances for each setting per year. The plot shows that, in the US, authenticity was performed much more frequently in campaign rallies than in other settings until mid-2000s. At that point, the frequency in which authenticity was performed across all settings in the US becomes more similar until the early-2010s. In the case of Brazil, we see a different trend. The frequency in which authenticity is performed in campaign rallies generally increased from the late 1980s to the mid-2010s. In fact, consistent with the findings above, there is a sharp increase in the frequency in which authenticity is performed across campaign rallies, debates, and in official speeches around the Rousseff years. We also see a sharp decrease in the frequency in which authenticity is performed across all setting from the mid-2010s onwards in Brazil.

```{r Figure 4, fig.cap="Authenticity Performances by Setting Time in Brazil and the US", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
aut_perf_setting <- US %>%
  select(-c(doc_id, text, settingc)) %>%
  group_by(date, setting) %>%
  summarise(across(everything(), sum)) %>%
  mutate(truth_telling = (truth/length)*1000,
         lie_accusations = (lies/length)*1000,
         consistency = (consistency/length)*1000,
         finger_pointing = (fpoint/length)*1000,
         origins = (origins/length)*1000,
         common_sense = (common_sense/length)*1000,
         anti_pc = (anti_PC/length)*1000,
         territory = (territory/length)*1000) %>%
  select(-c(length, truth, lies, fpoint,anti_PC))
aut_perf_set_long <- aut_perf_setting %>%
  tidyr::pivot_longer(consistency:anti_pc) %>%
  group_by(setting, date) %>%
  summarise(value = sum(value)) %>% 
  mutate(country = "US",
         date2 = stringr::str_extract(date, "[0-9]{2}$"))
aut_perf_setting_BR <- BR %>%
  select(-c(doc_id, text, settingc)) %>%
  group_by(date, setting) %>%
  summarise(across(everything(), sum)) %>%
  mutate(truth_telling = (truth/length)*1000,
         lie_accusations = (lies/length)*1000,
         consistency = (consistency/length)*1000,
         finger_pointing = (fpoint/length)*1000,
         origins = (origins/length)*1000,
         common_sense = (common_sense/length)*1000,
         anti_pc = (anti_PC/length)*1000,
         territory = (territory/length)*1000) %>%
  select(-c(length, truth, lies, fpoint,anti_PC))
aut_perf_set_long_BR <- aut_perf_setting_BR %>%
  tidyr::pivot_longer(consistency:anti_pc) %>%
  group_by(setting, date) %>%
  summarise(value = sum(value)) %>% 
  mutate(country = "Brazil",
         date2 = stringr::str_extract(date, "[0-9]{2}$"))
aut_perf_set_long_BR$date2 <- stringr::str_extract(aut_perf_set_long_BR$date, "[0-9]{2}$")
aut_perf_set_long_ap <- rbind(aut_perf_set_long, aut_perf_set_long_BR) %>% 
  mutate(Setting = factor(case_when(setting == 'interviews' ~ "Interview",
                                    setting == 'debates' ~ "Debate",
                                    setting == 'speeches' ~ "Official Speech",
                                    setting == 'campaign' ~ "Campaign Rally"),
                          levels = c("Official Speech", "Campaign Rally", "Debate", "Interview")))
ggplot(aut_perf_set_long_ap, aes(x = reorder(date2, as.numeric(date)),
                             y = value, color = Setting)) +
  geom_smooth(aes(group = Setting), se = FALSE) +
  facet_wrap(facets = "country", nrow = 2) +
  labs(x = "Year",
       y = "Normalized Value",
       title = "Authenticity Performances by Setting\nin Brazil and the US in Time",
       subtitle = "Normalized by number of characters per year in dataset",
       caption = "Curves in the plot are smoothed using loess method.") +
  theme_fivethirtyeight()

```

In Brazil and the US, authenticity has been performed less frequently on interviews, in comparison to other settings, from the early-2010s onwards. This could be related to the spread of social media whereas candidates have diverse outlets to interact with audiences, bypassing journalists, while performing authenticity to a wide variety of people. Moreover, in both cases, debates become a setting in which the frequency of authenticity performances generally increased in time. In fact, debates go from being the setting in which authenticity was least performed in the US in the early-1980s to become the setting in which it performed most by the late-2010s. As well, the frequency in which authenticity is performed in debates generally increased in Brazil in time, becoming the setting in which authenticity is most performed in the late-2010s. In both cases, debates are events televised to millions of voters. Debates give candidates the opportunity to discursively confront one another and attempt to convince undecided voters, though why and the extent to which they might matter for election outcomes is debatable (see McKinney and Warner 2013). In terms of authenticity performances, debates’ format requires candidates to answer quick and, as large-scale media events, become sources of “sticky” sound, text, and video bites charged with imagery, rather than meaning, that circulate to mark and represent political cycles in democracies [@foley2012,; @coleman2000]. As political bites become shorter, but more widespread, debates become ever important settings for a wide variety of performances.

# Conclusion

This article investigates how anti-PC discourses work in politics and how these types of discourses have changed over time. A brief review of the populism and cultural backlash scholarship illustrates how these literatures focus on specific manifestations of anti-PC discourses by specific leaders. Instead, this paper argues that anti-PC discourses in politics are authenticity performances that reduce the perceived link between thinking and saying for audiences (see Conway et al. 2009). Several other authenticity performances are also theorized. Individual authenticity performances, for example, derive plausibility from audiences' expectations about a political performer (or opponent) considering the information they have. These performances include claims of truth telling or consistency and lie accusations or finger pointing. Collective authenticity performances derive plausibility for performance based on the cultural connections shared between audiences and performer. These performances include anti-PC, pointing at origins, allusions to common sense, or claims of territorial knowledge. A framework for systematically investigating authenticity performances in politics that focuses on performative displays (what), projections (who, when, and where), and mechanisms (how) is established. Large text datasets on official speeches, campaign remarks, debates, and interviews for politicians at the national level for the US and Brazil since the 1980s are assembled by scraping repositories and YouTube. A dictionary of terms for investigating authenticity performances is built based on framework. This allows to identify, compare, and analyze how authenticity performances change in time, by politicians, and across political settings.

The analysis reveals several interesting patterns as, for instance, the total frequency of performances that promote oneself, as origins and truth-telling, is greater than performances that focus on average for both cases. Interestingly, the total frequencies of authenticity performances are not systematically greater in election years in comparison to non-election years. These findings indicate that incumbents might be more careful towards when, where, and how authenticity is performed during election years. Indeed, most politicians perform authenticities above the 95th percentile when they are candidates, before being elected a first time, or after having left office. However, in the case of Brazil, we see a spike in the frequency authenticity is performed in politics from 2010 to 2016, the Dilma Rousseff years. Women in politics, arguably, need to personally justify themselves and their public policy choices more frequently than the man in the sample. Moreover, the variation in types of authenticity performed in time and across cases indicate that contextual conditions make some types of performances more, or less, credible to audiences at certain junctures. In such, politicians adapt to perform authenticities audiences “want to hear”. Indeed, many authenticity performances appear in high frequencies for opposing, and associated, candidates in similar years. Finally, debates became the setting in which authenticities are performed most across cases, while interviews are the setting in which authenticity was performed least frequently, in both cases in recent years. Social media platforms give candidates diverse outlets to interact with audiences bypassing journalists in interviews, whereas debates are large-scale media events that produce “sticky” political bites charged with imagery that circulate more than ever in democracies.

Looking into politics as performance emphasizes the performer's role, the script, the stage, and the audience, rather than the content, while placing agency both with audiences and performers. Besides, it illuminates several avenues for further research as, for example, the likely relationship between gender and the frequencies and types of authenticity performed in politics. Investigating these gendered aspects of how authenticity is performed in politics can contribute to understanding how gender mediates authenticity perceptions for audiences in politics. Moreover, several influential presidents appear do not perform authenticity as frequent as candidates who have lost elections to them. Investigating when, how, and for whom, performing authenticity reaps electoral benefits, and not, is pressing to understanding voter’s decisions beyond individual political or policy preferences. In brief, thinking politics through performances present new lenses to analyzing how everyday politic are done. Authenticity performances, as a framework, is a less contentious alternative to understand what discourses, as anti-PC, are, how they change over time, and why they might matter for political outcomes.

# Appendix

````{=tex}
\begin{landscape}

```{r appendix 1, fig.cap="Authenticity Performances Codebook", echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}

codebook <- tibble::tibble("Authenticity Performance" = c('Truth Telling', 'Lying Accusing', 'Consistency' , 'Finger Pointing', 'Origins', 'Common Sense', 'Anti-PC', 'Territory'),
"Lexicon English" = c("am telling the truth, are telling the truth, is telling the truth, the truth is, this is the truth, not lying, not lies, no lies, not telling you lies, is honest, am honest, is being honest, are being honest, are honest, honesty, is sincere, are sincere, am sincere, is being sincere, are being sincere, is true, are true, not a liar, bottom of my heart, I swear, I reassure, we reassure, I assure, we assure, be assured, is truthful, are truthful, am truthful, is being truthful, are being truthful, I know that, is evident, are evident, I am sure, trust me, am frank, are frank, is frank, being frank, is upfront, are upfront, am upfront, being upfront, will come clean, am coming clean, are coming clean, is straightforward, are straightforward, being straightforward, believe me, I am certain, no bullshit, not bullshitting",
"not truth, not the truth, not true, aren’t true, isn’t true, being untruthful, is lying, are lying, is a liar, are liars, is dishonest, are  dishonest, being dishonest, is fake, are fake, being fake, is corrupt, are corrupt, full of lies, not sincere, not being sincere, isn’t sincere, aren’t sincere, not honest, not being honest, is cheating, is a cheater, are cheaters, are cheating, are tricking, is tricking, be deceived, is deceiving, are deceiving, are a hypocrite, is a hypocrite, are being a hypocrite, is being a hypocrite, is crooked, are crooked, is misleading, are misleading, has double-standards, are sneaky, is sneaky,  has two faces, two-faced, has double faces, double-faced, you are wrong, not correct, fooled by, do not believe, is misrepresenting, they misrepresent, is misrepresent, are misrepresent, pretends that, pretends to, is pretending, are pretending, keep pretending, breach your trust, breach of trust, is false, are false, being false, is misinforming, are misinforming, being misinformed, pretended, cut the crap, full of crap",
"we delivered, I delivered, check and see, I keep my word, we keep our word, I kept my word, we kept our word, I keep my promise, I kept my promise, we keep our promise, as promised, we kept our promise, am responsible, I take responsibility, we take responsibility, we assume responsibility, we are accountable, we are responsible, our duty, my duty, give my word, giving my word, own up my, owning up my, accept responsibility, accept the blame, recognize my mistakes, admit I was wrong, I made mistakes, I guarantee, we guarantee, I can guarantee, we can guarantee, I promise, we promise, we can prove, I can prove, we proved, I proved, am reliable, rely on me, rely on us, be reassured, you can hold me accountable, you can hold us accountable, see with your own eyes, vote of confidence, our mission, my mission, my commitment, our commitment, during our government, during my government, while I was in charge",
"are inconsistent, is inconsistent, being inconsistent, are irresponsible, is irresponsible, being irresponsible, their fault, not my fault, not our fault, they left us with, they are responsible, are not responsible, aren’t responsible, is not responsible, isn’t responsible, costed us, false promises, lack accountability, lacking accountability, not kept their word, not kept his word, not kept her word, not kept promises, not kept the, not kept his, not kept her, not kept their, not keep their word, not keep his word, not keep her word, not keep the, didn’t keep the, didn’t keep her, didn’t keep his, hasn’t kept his, hasn’t kept her, not recognize, he made mistakes, she made mistakes, they made mistakes, not our mistake, not my mistake, not take responsibility, not my responsibility, not accountable, him accountable, them accountable, her accountable, blame them, blame him, blame his, blame her, their blame, break promises, broken promises, has betrayed, they betrayed, betraying, will betray, has tricked, has lied, not deliver, didn’t deliver, hasn’t deliver, failed your obligations, failed in your obligations, failed his obligations, failed her obligations, failed in his duty, failed in her duty, failed his duty, failed her duty, failed your duties, stabbed in the back",
"I was born, I come from, we come from, I grew up, growing up in, my parents, my mom, my mother, my father, my dad, my family, raised me, I was raised, we were raised, we grew up, my background, being surrounded by, being exposed to, my siblings, going to school in, our local church, Sunday mass, Saturday mass, family tradition, tradition in my house, in our house, growing up, back in the day, my grandparents, in my town, in my state, in my region, our community, in my community, our town, our state, my hometown, our hometown, my home state, our home state, back home, our house, my house, our neighbourhood, in my district, I lived in, we lived in, we used to play, I used to play, I was thought",
"is common sense, are common sense, everyone knows, it is undeniable, stating the obvious, say the obvious, everyone agrees, we all know, common wisdom, the people know, popular knowledge, from experience, it is my experience, sound judgment, practical solution, practical choice, practical answer, pragmatic solution, pragmatic answer, pragmatic choice, realistic answer, let me tell you about, is obvious, are obvious, obvious answer, obvious solution, as we all learned, we have all learned that, do not need to tell you that, the reality is, there is no logic, it does not make sense, it doesn’t make sense, we know it does not work, no one disagrees that, no person disagrees, there is not a person, there is not a human being, there is not a family, there is not an American, there is no single citizen, there is not one single person, there is not one single human being, there is not one single family, there is not one single American, there is not one single citizen, there is not one single person, there is not one human being, there is not one family, there is not one American",
"politically correct, political correctness, PC, plain speaking, speaking my mind, speak my mind, say what I think, saying what I think, not going to pretend, not pretend, speak what you think, not what you want to hear, not butter up, not beat around the bush, cut to the chase, just being real, saying what everyone thinks, say what everyone is thinking, speaking plainly, coloured people, negro, retarded, nigger, third world, oriental people, crippled people, is crippled, culturally deprived, drug addict, junkie, drunk, fat people, fat person, fat population, handicapped, homosexual faggot, deviant, perverted, illegals, illegal immigrants, illegal alien, Jew, non-white, prostitutes, promiscuous, stupid, tribe, underdeveloped",
"have been to, have visited, came all the way to, back from, will visit, saw first-hand, see first-hand, we visited, I visited, we visited, travelled to, traveling to, spend a few days in, spent some time in, spent time in, met great people in, we were hosted, I was hosted, our time in, my time in, our visit, spent a lot of time in, were many times in, got to know the whole country, got to know all the states"),
"Lexicon Portuguese" = c("a verdade e, esta e a verdade, digo a verdade, dizemos a verdade, pura verdade, não e mentira, não estou mentindo, e honesto, sou honesto, somos honesto, sendo honesto, a honestidade, ser sincero, e sincero, com sinceridade, e verdade, são verdadeiras, não sou mentiroso, não minto, fundo do meu coração, sou verdadeiro, somos verdadeiros, tenho certeza, certeza absoluta, confia em mim, confie em mim, pode confiar, sou franco, somos francos, fraqueza, falando a verdade, falo a verdade, falamos a verdade, acredite em mim, pode acreditar, podem acreditar, eu tenho certeza, isso e a verdade, somos honestos, com honestidade, toda a sinceridade, com sinceridade, toda sinceridade, sou confiável, somos confiáveis, as coisas são assim, a realidade das coisas, juro por deus, com certeza, digo com precisão, veracidade, premissa, afirmo para vocês, isso e como aconteceu, falar umas verdades",
"não e verdade, não e verdadeiro, e mentiroso, está mentindo, são mentiroso, e mentira, de mentira, tudo mentira, e desonesto, mentiram, mentiu, um desonesto, esse desonesto, de desonesto, são desonesto, e falso, são falsos, são corruptos, e corrupto, de corrupto, todos corrupto, não são sincero, não e sincero, não são honestos, não e honesto, são trapaceiros, e trapaceiro, eles trapaceiam, trapaceou, e enganar, ser enganado, vão enganar, sendo enganados, e hipócrita, e enganador, e enganação, duas caras, enganado por, não acredite, eles finge, ele finge, e fingimento, ela finge, quebrou a sua confiança , quebra de confiança,  e falso, são falsos, falsidade, e ficção, história para boi dormir, historinha para boi dormir, e calunia, são calunias, difamação, difamar, uma inverdade, são inverdades, e inverdade, isso e invenção, essas são invenções, isso e uma lenda, essas são ledas, tenta iludir, tentando iludir, uma farsa, tramoia, mal intencionado, mas intenções, falta de informação, esta mal-informado, estão mal-informados",
"nós entregamos, eu entreguei, veja com seus próprios olhos, cumpro minhas palavras, cumprimos nossas palavra, cumpri minha palavra, cumpro minhas promessas, nossas promessa, um compromisso, meu compromisso, tenho um compromisso com, eu sou responsável, eu assumo a responsabilidade, nós somos responsáveis, nós assumimos a responsabilidade, nosso dever, meu dever, dou minha palavra, faço uma promessa, fazer uma promessa, aceitar a responsabilidade, aceito a responsabilidade, aceitamos a responsabilidade, aceitar a culpa, meus erros, que errei, eu errei, eu garanto, eu posso garantir, eu prometo, podemos provar, posso provar, provaremos, eu provei, voto de confiança, encarrego pessoalmente, encarreguei pessoalmente, estou comprometido, meu comprometimento, comprometimento com, o comprometimento, fazer o possível, minha supervisão, minha missão, nossa missão, no meu governo, no nosso governo, durante nosso governo, eu era encarregado, eu era o encarregado, fomos encarregados de",
"e inconsistente, são inconsistente, e irresponsável, são irresponsáveis, culpa deles, a culpa não e minha, não e minha culpa, eles nós deixaram, são responsáveis, e responsável, nós custou, falsas promessas, falta de prestação de contas, falharam, falhou, não cumpriu, não cumpriram, não reconheceu, não reconheceram, errou, erraram, não se responsabiliza, não me responsabilizo, culpa e sua, sua culpa, quebrar promessas, promessas quebradas, quebra de promessas, fala uma coisa e faz outra, fala uma coisa aqui e faz outra, falsas promessas, são trapaceiros, cometeu erros, cometeram erros, não reconhece, não reconheceu, assumiu a responsabilidade, promete uma coisa, promete o mundo, traiu a confiança, traiu a sua confiança, quebra de confiança, quebraram sua confiança, e falcatrua, foi falcatrua, cheio de falcatrua, houve fraude, houveram fraudes, fraudulento, uma negociata, facada nas costas, faltou com respeito, não faz o que promete, não fez o que promete, promessas em vão, palavras em vão, falta de comprometimento, falta de compromisso, houveram desvio, houve desvio, a culpa e do, cheio de promessas, a conta não fecha, não terminaram",
"Eu nasci, Eu vim de, eu venho de, viemos de, cresci, nós crescemos, meus pais, minha mãe, minha mãe, minha família, fui criado, fomos criados, minhas origens, meus irmãos, meu irmão, minha irmã, tradição familiar, tradição em casa, crescendo, antigamente, meu avô, minha avó, meus avós, na minha cidade, no meu estado, na minha região, nossa comunidade, na minha comunidade, nossa cidade, nosso estado, cidade natal, estado de origem, minha casa, nossa casa, lá em casa, nosso bairro, no meu bairro, eu morava, vivíamos, na minha terra, de onde eu venho, missa de domingo, missa toda semana, brincava, eram outros tempos, fui educado, morávamos, eu morei, nós moramos, de onde venho, eram tempos diferentes",
"senso comum, bom senso, todos sabem, afirmando o óbvio, todos concordam, todos sabemos, sabemos todos, todos nós sabemos, sabedoria popular, por experiência, e minha experiência, sou prático, tem que ser prático, devemos ser prático, sendo prático, sou pragmático, tem que ser pragmático, devemos ser  pragmático, sendo pragmático, sou realista, sendo realista, sejamos realista, realisticamente falando, e óbvio, como todos nós aprendemos, como sabemos, não preciso te dizer, o povo sabe, agente aprendeu, nós aprendemos, nós sabemos, não tem logica, como aprendemos, não faz sentido, não fazem sentido, estamos cansados de saber, sabemos que não funciona, ninguém discorda que, não tem uma pessoa, não existe uma pessoa, não há uma pessoa, não existe um ser humano, não tem um ser humano, não há um ser humano, não tem uma família, não existe uma família, não há uma família, não tem um brasileiro, não há um Brasileiro, não existe um brasileiro, não tem uma brasileira, não há uma Brasileira, não existe uma brasileira",
"politicamente correto, falar francamente, falando francamente, falar o que penso, falo o que penso, falando o que penso, dizer o que penso, papas na língua, não vou fingir, não estou aqui para agradar, falar o que você pensa, o que você quer ouvir, não adulterar, não rodeio, não dou rodeio, direto ao ponto, dizer o que todos pensam, dizendo o que penso, dizendo o que todos pensam, dizer o que todos estão pensando, não vou amaciar, não dá para amaciar, gordos, retardado, retardada, veado, população preta, os pretos, as pretas, terceiro mundo, viciado em drogas, bêbado, drogado, sem cultura, pervertidos, promíscuo, imbecil, estupido, aleijado, defeituoso, incapacitado, inválido, mongoloide, deficiente mental, deficiência mental, o incapacitado, a incapacitada, travesti, homossexualismo",
"estive em, visitei, voltou de, voltei de, voltando de, voltamos de, estive em, estivemos em, visitará, visitarei, vi em primeira mão, ver em primeira mão, visitamos, viajei para, passei alguns dias em, passei algum tempo em, passei um tempo, conheci ótimas pessoas, conhecemos ótimas pessoas em, fomos hospedados, minha passagem, nossa passagem, nossa visita, fui muitas vezes para, estive muitas vezes em, passei muito tempo em, meu tempo em, estive por todo o Brasil, de norte a sul do pais, conheço todo o pais, conheci todo o pais, conheci todo o Brasil, conheço todo o Brasil"))
codebook$`Lexicon Portuguese` <- stringi::stri_trans_general(codebook$`Lexicon Portuguese`,
                                                             id = 'latin-ascii')
kbl(codebook, booktabs = T, longtable = TRUE,
    caption = "Authenticity Performances Codebook") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"),                    
                position= "center", font_size = 7, full_width = TRUE) %>%
  column_spec(1, width="2cm", bold=TRUE) %>%
  column_spec(2, width="6cm") %>%
  column_spec(3, width = "8cm")
```

\end{landscape}
````

````{=tex}
\begin{landscape}

```{r appendix 2, fig.cap="Appendix 2 - Authenticity Performances by Setting in Brazil and the US", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
check_setting_US <- plm::plm(value ~ Setting,
                             data = filter(aut_perf_set_long_ap, country == "US"),
                             model = "within", index = c("date"))
check_setting_BR <- plm::plm(value ~ Setting,
                             data = filter(aut_perf_set_long_ap,
                                           country == "Brazil"),
                             model = "within",
                             index = c("date"))
modelsummary::modelsummary(list("Brazil" = check_setting_BR, "US" = check_setting_US),
                           stars = TRUE, title = "Authenticity Performances by Setting in Brazil and the US")
```

\end{landscape}
````

# References
